\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-20 document/ms.tex
Edited last paragraph in section 5 with further caveats

The occurrence rates given here should be interpreted with a few caveats in
mind.
First, when we inferred the periods of the planets with only one transit, we
assumed that the period was long enough that no other transit occurred during
the \kepler\ lifetime.
This neglects the small but non-negligible posterior probability~--~less than
one percent for the typical candidate~--~that a second transit might have
occurred in a data gap.
All of the candidates in our catalog are consistent with having periods this
long but the geometric transit probability decreases quickly with orbital
period.
For the purposes of this \paper, we neglect this effect because its rigorous
treatment is subtle, but comment that this would only ever decrease the
occurrence rate estimate.

>>>>

The occurrence rates given here should be interpreted with a few caveats in
mind.
First, when we inferred the periods of the planets with only one transit, we
assumed that the period was long enough that no other transit occurred during
the \kepler\ lifetime.
This neglects the small but non-negligible posterior probability~--~less than
one percent for the typical candidate~--~that a second transit might have
occurred in a data gap.
All of the candidates in our catalog are consistent with having periods this
long but the geometric transit probability decreases quickly with orbital
period.
For the purposes of this \paper, we neglect this effect because its rigorous
treatment is subtle, but comment that this would only ever decrease the
occurrence rate estimate.   Second, we assume that each planet candidate transits
the star that is characterized by \citet{Huber:2014}; i.e., that each planet
does not transit a fainter companion star or a background star.  If the planet
does transit a companion star, then the companion star must be fainter, and hence
denser, causing the period estimate to be underestimated.  If the planet transits
a background star, it is more likely to be a giant star due to Malmquist bias,
hence the density of the star and period of the planet would be overestimated. 
Either of these scenarios has a small
probability, so we expect that our population estimates will stand, while
the parameter estimates for individual candidates should be taken as provisional
until more detailed follow-up is carried out, including high-contrast imaging,
high-resolution spectroscopy, and parallax measurements.  Third, we assume
that the \citet{Huber:2014} parameters are accurate for each star that is transited by
a planet candidate, and that each transit is unaffected by blending.
Malmquist bias, Eddington bias, and metallicity bias may affect the stellar parameters
\citep{Gaidos:2012}, and so we again caution that the individual parameter
estimates should be taken as provisional until more detailed follow-up is
completed.
